---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
load the libraries, then unzip and then read the Activity file:
```{r}
library(ggplot2)
library(dplyr)
unzip("activity.zip")
activity<-read.csv("activity.csv")
```

print some statistics about the file
```{r}
summary(activity)

head(activity)
```

The 'steps' column contains a rather large fraction of NA's. 
It's a good idea to see where they occur 
```{r}
NA_activity<-activity[is.na(activity$steps),]
qplot(date,interval,data=activity,color=is.na(steps))
```

it seems that only complete days are missing 


## What is mean total number of steps taken per day?

```{r}
activityByDay <- group_by(activity,date)
totalStepsByDay<-summarise(activityByDay,totalsteps=sum(steps))
mean(totalStepsByDay$totalsteps,na.rm=TRUE)
```


## What is the average daily activity pattern?
```{r}
activityByInterval <- group_by(activity,interval)
averageStepsByInterval<-summarise(activityByInterval,averagesteps=mean(steps,na.rm=TRUE))
qplot(interval,averagesteps,data=averageStepsByInterval)
```


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
